Uncertainty propagation in neural networks for sparse coding

### 2018-11-29 nips_workshop_2018/poster/BayesianLISTAposter.tex
add logos

\title{Uncertainty propagation in neural networks for sparse coding}   \institute{University of Sheffield, UK, University of Oxford, UK }
\author{Danil Kuzin, Olga Isupova, Lyudmila Mihaylova}   \titlegraphic{Logo}
\usetheme{Autumn}
\usecolorstyle{Britain}
\begin{document}
  \maketitle
  \begin{columns}
    \column{0.5}
    \block{1-LISTA}{
      \begin{minipage}[t]{0.55\linewidth}
        \vspace{0.1in}
        \coloredbox{
          Estimate \(\boldsymbol\beta \) from observations \(\mathbf{y}\) collected as \(\mathbf{y} = \mathbf{X} \boldsymbol\beta + \boldsymbol\varepsilon\), s.t.\ elements \(\boldsymbol\beta \) contain zeros. 
        }
      \end{minipage}
      \begin{minipage}[t]{0.4\linewidth}
        \begin{tikzfigure}
          \includegraphics[width=400pt]{graphics/sparse_problem.pdf}
        \end{tikzfigure}
      \end{minipage}

>>>>

\title{Uncertainty propagation in neural networks for sparse coding}   
\institute{University of Sheffield, UK, University of Oxford, UK }
\author{Danil Kuzin, Olga Isupova, Lyudmila Mihaylova}   
\titlegraphic{\includegraphics[width=0.25\textwidth]{graphics/University_of_Sheffield_coat_of_arms}
\vspace{-1in}\includegraphics[width=0.247\textwidth]{graphics/oxford_coat_of_arms}}
\usetheme{Autumn}
\usecolorstyle{Britain}

\makeatletter
\renewcommand\TP@maketitle{%
    \begin{minipage}{0.2\linewidth}
       \centering
       \@titlegraphic
    \end{minipage}
    \hfill
   \begin{minipage}{0.8\linewidth}
        \centering
        \color{titlefgcolor}
        {\bfseries \Huge \sc \@title \par}
        \vspace*{1em}
        {\huge \@author \par}
        \vspace*{1em}
        {\LARGE \@institute}
    \end{minipage}%
}
\makeatother

\begin{document}
  \maketitle
  \begin{columns}
    \column{0.5}
    \block{1-LISTA}{
      \begin{minipage}[t]{0.55\linewidth}
        \vspace{0.1in}
        \coloredbox{
          Estimate \(\boldsymbol\beta \) from observations \(\mathbf{y}\) collected as \(\mathbf{y} = \mathbf{X} \boldsymbol\beta + \boldsymbol\varepsilon\), s.t.\ elements \(\boldsymbol\beta \) contain zeros. 
        }
      \end{minipage}
      \begin{minipage}[t]{0.4\linewidth}
        \begin{tikzfigure}
          \includegraphics[width=400pt]{graphics/sparse_problem.pdf}
        \end{tikzfigure}
      \end{minipage}
